Illusory Finger Stretching and Somatosensory Responses

### 2025-06-16 manuscript.qmd
Added code to download missing resources

>>>>

if (!file.exists('Figures/Pilot Data 2.png')){
  osfproject <- osf_retrieve_node("wfu7j")
  osffiles <- osf_ls_files(osfproject,n_max=20)
  fid <- which(osffiles$name=='Pilot Data 2.png')
  osf_download(osffiles[fid,], path='Figures/',progress=TRUE)
}

if (!file.exists('Figures/Pilot Data 3.png')){
  osfproject <- osf_retrieve_node("wfu7j")
  osffiles <- osf_ls_files(osfproject,n_max=20)
  fid <- which(osffiles$name=='Pilot Data 3.png')
  osf_download(osffiles[fid,], path='Figures/',progress=TRUE)
}

if (!file.exists('Figures/Hypotheses Schematic.png')){
  osfproject <- osf_retrieve_node("wfu7j")
  osffiles <- osf_ls_files(osfproject,n_max=20)
  fid <- which(osffiles$name=='Hypotheses Schematic.png')
  osf_download(osffiles[fid,], path='Figures/',progress=TRUE)
}
